---
title: "R Project 1 - Hello R"
author: "Aneeka Khan"
date: "Due pls have mercy on me (:"
output: 
  html_document: 
    theme: yeti
    fig_width: 6
    fig_height: 4
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows and 3 columns, and the columns are the variables.

### Exercise 2

The data is giving us multiple  x and y coordinates through which a dinosaur is being plotted and hence the cute picture.

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

This code is plotting the correlation coefficient among the points which is essentially the linear association between the two variables that we plotted. 

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


The data is plotting a star. I replaced the dino in the above variable with star and boom, a star appears.

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

The data is creating a table with the correlation coefficient.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

The data is plotting a circle using multiple x and y coordinates.

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```
The data is creating a table with the correlation coefficient.
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5
plot every data set

``` {r grand finale}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

find the correlation coeff of every data set

``` {r cor}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(26)
```

